ANTS: Advanced Open-Source Tools for Normalization And Neuroanatomy

### 2009-06-11 Documentation/Tex/metric.tex
need Figures/r16...
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@24 fd2da0a4-d968-48df-9cb5-d8c496287cbf
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@32 fd2da0a4-d968-48df-9cb5-d8c496287cbf

%        \begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}
    \label{fig:metric_example}
    \centering
    \begin{tabular}[h]{c|c|c}
        \includegraphics[width=0.16\textwidth]{Figures/r16slice.jpg} &
        \includegraphics[width=0.16\textwidth]{Figures/r64slice.jpg} &
        \includegraphics[width=0.16\textwidth]{Figures/resMSQ.jpg} \\
        fixed image &
        moving image & 
        MSE  \\
    \end{tabular} 
    \itkcaption{registration using mean square intensity difference}
\end{figure}
    %    \end{wrapfigure}
Here is an example script to register a pair of images using different image metrics:
\begin{verbatim}
#use cross-correlation with cc region radius 2
ANTS 2 -m CC[r16slice.nii,r64slice.nii,1,2] -r Gauss[3,0] -t SyN[1] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resCC2.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resCC2.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resCC2.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resCC2.nii metricexamplelog.txt
ConvertToJpg resCC2.nii resCC2.jpg

#use cross-correlation with cc region radius 4
ANTS 2 -m CC[r16slice.nii,r64slice.nii,1,4] -r Gauss[3,0] -t SyN[1] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resCC4.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resCC4.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resCC4.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resCC4.nii metricexamplelog.txt
ConvertToJpg resCC4.nii resCC4.jpg

#use cross-correlation with cc region radius 2
ANTS 2 -m PR[r16slice.nii,r64slice.nii,1,2] -r Gauss[3,0] -t SyN[1] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resPR2.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resPR2.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resPR2.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resPR2.nii metricexamplelog.txt
ConvertToJpg resPR2.nii resPR2.jpg

#use cross-correlation with cc region radius 4
ANTS 2 -m PR[r16slice.nii,r64slice.nii,1,4] -r Gauss[3,0] -t SyN[1] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resPR4.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resPR4.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resPR4.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resPR4.nii metricexamplelog.txt
ConvertToJpg resPR4.nii resPR4.jpg

#use intensity difference with radius 0 -- radius no effect on intensity difference
ANTS 2 -m MSQ[r16slice.nii,r64slice.nii,1,0] -r Gauss[3,0] -t SyN[0.5] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resMSQ.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resMSQ.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resMSQ.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resMSQ.nii metricexamplelog.txt
ConvertToJpg resMSQ.nii resMSQ.jpg

# use mutual information with radius 0 and step-size 1.0
ANTS 2 -m MI[r16slice.nii,r64slice.nii,1,32] -r Gauss[3,0] -t SyN[1] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resMI2.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resMI2.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resMI2.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resMI2.nii metricexamplelog.txt
ConvertToJpg resMI2.nii resMI2.jpg

\end{verbatim}

>>>>

%        \begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}
    \label{fig:metric_example}
    \centering
    \begin{tabular}[h]{c|c|c}
%        \includegraphics[width=0.16\textwidth]{Figures/r16slice.jpg} &
%        \includegraphics[width=0.16\textwidth]{Figures/r64slice.jpg} &
 %       \includegraphics[width=0.16\textwidth]{Figures/resMSQ.jpg} \\
        fixed image &
        moving image & 
        MSE  \\
    \end{tabular} 
    \itkcaption{registration using mean square intensity difference}
\end{figure}
    %    \end{wrapfigure}
Here is also an example script to register a pair of images using mean square intensity difference and computing the metrics of the registration image.
\begin{verbatim}
#use intensity difference with radius 0 -- radius no effect on intensity difference
ANTS 2 -m MSQ[r16slice.nii,r64slice.nii,1,0] -r Gauss[3,0] -t SyN[0.5] -i 50x50x30
WarpImageMultiTransform 2 r64slice.nii resMSQ.nii Warp.nii Affine.txt
MeasureImageSimilarity 2 0 r16slice.nii resMSQ.nii metricexamplelog.txt
MeasureImageSimilarity 2 1 r16slice.nii resMSQ.nii metricexamplelog.txt
MeasureImageSimilarity 2 2 r16slice.nii resMSQ.nii metricexamplelog.txt
ConvertToJpg resMSQ.nii resMSQ.jpg
\end{verbatim}
